The hidden manifold distance for functional manifold data

### 2019-06-24 index.Rmd
added (3!) versions of tecator dataset

###  Real data
A few examples of the datasets used by functional classification papers

* Wheat, rainfall and phoneme in "Achieving near-perfect classification for functional data"
* Berkeley growth curves in Chen et. al 2014, Biometrics.
* Tecator and phoneme in technometrics paper.

>>>>

###  Real data
Datasets used by functional classification papers

* Wheat, rainfall and phoneme in Aurore's paper "Achieving near-perfect classification for functional data"
* Berkeley growth curves in Chen et. al 2014, Biometrics.
* Tecator and phoneme in Mahalanobis technometrics paper.

Datasets used in functional manifold papers
* Berkeley growth, yeast cell cycle gene expression in Chen and Muller
* Tecator in Lin and Yao's contamination paper
* Berkeley growth, gait cycle in Jean-Michel Loubes' robust isomap paper
